\documentclass{article}
\usepackage{amsmath}
\usepackage[utf8]{inputenc}
\usepackage{booktabs}
\usepackage{microtype}
\usepackage[colorinlistoftodos]{todonotes}
\pagestyle{empty}

\title{Gorilla Report}
\author{Author 1 and Author 2}

\begin{document}
  \maketitle

  \section{Results}

  \todo[inline]{Briefly comment the results, did the script say all your solutions were correct? Approximately how long time does it take for the program to run on the largest input? What takes the majority of the time?}

  \section{Implementation details}

  \todo[inline]{How did you implement the solution? Which data structures were used? Which modifications to these data structures were used? What is the overall running time? Why?}

\end{document}

• Is your solution recursive or iterative?
	recursive skickar upp saker tillbaka medan iterativ löser en del och sedan går vidare, alltså är den rekrusiv
• What is the time complexity, and more importantly why?
	O(n*m)
• What would the time complexity of a recursive solution without cache be?
	varje steg finns det tre möjligheter, det tar max n+m steg, O(3^(n+m))
• Can you think of any applications of this type of string alignment?
	DNA-alignment? Auto-correct
• What could the costs represent in the applications?
	Desto närmare tangenter är på tangentbordet, ju störe chans är det att det var ett stavfel och inte ett nytt ord. 
	kanske kan ha en datorbas med kända ord som sedan försökes passas till ordet som skrevs och dem med minst kostand är nog det ordet som försöktes skrivas.